Near Optimal Behavior with Approximate State Abstraction

### 2016-02-02 paper/theory_results.tex
a few small cleanups in the proofs

\begin{align*}
B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|
\end{align*}
\begin{multline*}
\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)} \\ \left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]
\end{multline*}
By the similarity of transitions of grouped states under $\epM$:
\begin{align*}
 \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}\\
&\text{Applying 0-1 reward normalization and algebra:}\\
 \leq & \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
\end{align*}

@@

{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
\end{equation}

@@

{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
\end{equation}

>>>>

\begin{align*}
B = &\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a} |Q(s_1, a) - Q(s_2, a)|\\
=&\max_{s_A \in \mcS_A, s_1, s_2 \in X(s_A), a}      |R(s_1, a) - R(s_2, a) +\\
& \gamma \sum_{g' \in \mcS_G}(\mcT(s_1,a,g')-\mcT(s_2, a, g'))\max_{a'}Q(g', a')|
\end{align*}
\begin{multline*}
\leq \epsilon + \gamma \sum_{s_A \in \mcS_A}\sum_{g' \in X(s_A)} \\ \left[(T(s_1, a, g')-T(s_2, a, g')) 		\max_{a'}Q(g', a')	\right]
\end{multline*}
By the similarity of transitions of grouped states under $\epM$:
\begin{align*}
 \leq &\epsilon + \gamma Q_{max} \sum_{s_A \in \mcS_A} \epsilon \\
\leq& \epsilon + \gamma|\mcS_G|\epsilon Q_{max}
\end{align*}
Applying 0-1 reward normalization and algebra:
\begin{equation*}
 \leq \frac{\epsilon + \gamma(|\mcS_G| - 1) \epsilon}{1-\gamma}
\end{equation*}

@@

{\bf Lemma 3:} When $S_A$ is created using a function of the $\ep_{mult}$ type, for some constant positive $k \in \mathbb{R}$:
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\left(\textsc{QMax}|\mathcal{A}| + k \epsilon + k \epsilon^2\right)}{1-\gamma}:
\end{equation}

@@

{\bf Lemma 4:} When $S_A$ is created using a function of the $\ep_{bolt}$ type, for some constant positive $k \in \mathbb{R}$::
\begin{equation}
\forall_{s \in S_M} : | V^{\pi^*_G}(s) - V^{\pi^*_{A}}(s) | \leq \frac{\epsilon(\textsc{QMax}|\mathcal{A}| + k\epsilon) + A}{1-\gamma}:
\end{equation}
